% cv example for classicthesis.sty
\documentclass[10pt,a4paper]{scrartcl}
\usepackage[LabelsAligned]{currvita} % nice cv style
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage[nochapters]{classicthesis}

\renewcommand*{\cvheadingfont}{\LARGE\color{Maroon}}
\renewcommand*{\cvlistheadingfont}{\large\color{RoyalBlue}}
\renewcommand*{\cvlabelfont}{\qquad}
\areaset[5mm]{345pt}{684pt}% 609 + 33 + 42 head \the\footskip
%335
%\setlength{\cvlabelwidth}{50mm}%LabelsAligned
%\setlength{\textwidth}{20cm}%LabelsAligned
%\setlength{\cvlabelsep}{50mm}%LabelsAligned
%\setlength{\marginparwidth}{7.5em}%
%\setlength{\marginparsep}{10em}%
\AtBeginDocument{% 
    \settowidth{\cvlabelwidth}{%
        \cvlistheadingfont Student Researcher %
    }%
}

\hypersetup{%
    colorlinks=true, linktocpage=true, pdfstartpage=3, pdfstartview=FitV,%
    breaklinks=true, pdfpagemode=UseNone, pageanchor=true, pdfpagemode=UseOutlines,%
    plainpages=false, bookmarksnumbered, bookmarksopen=true, bookmarksopenlevel=1,%
    hypertexnames=true, pdfhighlight=/O,%hyperfootnotes=true,%nesting=true,%frenchlinks,%
    urlcolor=webbrown, linkcolor=RoyalBlue, citecolor=webgreen, %pagecolor=RoyalBlue,%
    % uncomment the following line if you want to have black links (e.g., for printing)
    %urlcolor=Black, linkcolor=Black, citecolor=Black, %pagecolor=Black,%
    pdftitle={Cameron Bracken's Resume},%
    pdfauthor={Cameron Bracken},%
    pdfsubject={},%
    pdfkeywords={},%
    pdfcreator={pdfLaTeX},%
    pdfproducer={LaTeX with hyperref and classicthesis}%
}

\begin{document}
    \begin{cv}{\spacedallcaps{Curriculum Vit\ae}}
        \pdfbookmark[1]{Cameron Bracken}{info}
        \begin{cvlist}{}\label{info}  
            \item   Cameron Bracken
            \item 925.548.7392
            \item   \url{cameron.bracken@gmail.com}
            %\item   925.548.7392
            %\item   \url{http://www.linkedin.com/pub/cameron-bracken/20/31b/996}
        \end{cvlist}
        
        \pdfbookmark[1]{Education}{edu}
        \begin{cvlist}{\spacedlowsmallcaps{Education}}\label{edu}
            \item[M.S.] \textbf{University of Colorado at Boulder}: { Civil, Environmental and Architectural Engineering, Department of Hydrology, Water Resources, and Environmental Fluid Mechanics},  2011
            \item Thesis: ``Seasonal to Inter-Annual Streamflow Simulation and Forecasting on the Upper Colorado River Basin and Implications for Water Resources Management''
            \item[B.S.] \textbf{Humboldt State University}: {Environmental Resources Engineering}, 2009
            \item[B.S.] \textbf{Humboldt State University}: {Applied Mathematics}, 2009
        \end{cvlist}
        
        \pdfbookmark[1]{Experience}{exp}
        \begin{cvlist}{\spacedlowsmallcaps{Experience}}\label{exp}
            {\setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
            \setlength{\parsep}{0pt}
            
            \item[2009 - 2011] Graduate Research Assistant Center for Advanced Decision Support for Water and Environmental Systems
            }
            \item[2008] Student Researcher, National Weather Service, Eureka CA
            \item[2007] Student Researcher, Environmental Fluids Research Experience for Undergraduates, University of Colorado at Boulder
        \end{cvlist}
        
        \pdfbookmark[1]{Research Interests}{interests}
        \begin{cvlist}{\spacedlowsmallcaps{Research Interests}}\label{interests}
            \item[] Stochastic Hydrology, Time series modeling, Forecasting, 
        \end{cvlist}
        
        \pdfbookmark[1]{Teaching \& Tutoring}{tut}
        \begin{cvlist}{\spacedlowsmallcaps{Teaching \& Tutoring}}\label{tut}
            \item[Fall 2009] Lead TA ENGR 4333: Engineering Hydrology. 
            \item[2004 -- 2011] Various private tutoring, Algebra -- Calculus III.
        \end{cvlist}
        
        \pdfbookmark[1]{Awards}{awards}    
        \begin{cvlist}{\spacedlowsmallcaps{Awards}}\label{awards}
            \item   \textit{Department Fellow}, Civil, Environmental and Architectural Engineering, 2009 - Present
            \item   \textit{Best Undergraduate Research Project}, Humboldt State University, Spring 2009
            \item   \textit{Homer Arnold Award} in Applied Engineering for outstanding achievement in applied engineering design involving environmental and resource problems, Humboldt State University, Spring 2009 
            \item   \textit{Roscoe-Schneller Award} for outstanding potential in Environmental Resources Engineering, Humboldt State University, Spring 2007 (\$500).

	        \item \textit{Robert S. Chambers Award} for academic achievement in mathmatics, Humboldt State University, Spring 2007 (\$500).

	        \item \textit{Honorable mention}, 2007 COMAP Mathematical Contest in Modeling (MCM).
	
	        \item \textit{Honorable mention}, 2008 COMAP Mathematical Contest in Modeling (MCM).
        \end{cvlist}
        
        \pdfbookmark[1]{Publications}{pub}    
        \begin{cvlist}{\spacedlowsmallcaps{Publications}}\label{pub}
	        \item Bracken, C., B. Rajagopalan, and E. Zagona (2011), A Nonstationary Hidden Markov Model for Stochastic Streamflow Simulation and Short Term Forecasting in the Upper Colorado River Basin, {\it Submitted to Water Resour. Res.}
	        \item Bracken, C., E. Zagona, B. Rajagopalan. A New Probabilistic Model for Reservoir Operations in the Upper Colorado River Basin, {\it Submitted to Journal of Hydrology.}
            \item   Bracken, C., B. Rajagopalan, and J. Prairie (2010), A multisite seasonal ensemble streamflow forecasting technique, Water Resour. Res., 46, W03532, doi:10.1029/2009WR007965.
           
         \end{cvlist}

        \pdfbookmark[1]{Software}{software}    
        \begin{cvlist}{\spacedlowsmallcaps{Software}}\label{software}
            \item Charlie Sharpsteen and Cameron Bracken (2011). \textit{tikzDevice: A Device for R Graphics Output in PGF/TikZ Format.}  R package version 0.6.1.
            \item Cameron Bracken  and Charlie Sharpsteen (2011). \textit{pgfSweave: Quality speedy graphics compilation and caching with Sweave.} R package version 1.2.1.
        \end{cvlist}

        \pdfbookmark[1]{Presentations}{pres}    
        \begin{cvlist}{\spacedlowsmallcaps{Presentations}}\label{pres}
        	\item {\it A Nonstationary Hidden Markov Model for Stochastic Streamflow Simulation and Inter-annual Forecasting in the Upper Colorado River Basin}, AGU Fall Meeting 2011, H51N. Medium- to Long-Range Water Resources Forecasting from Regional to Global Scale, Dec. 9, 2011.
            \item \textit{Large Scale Hydrology and Water Resources in the Upper Colorado River Basin}. Guest Lecture, Mountain Geography, May, 2011.
            \item \textit{Interannual Forecasting of Upper Colorado River Flow}. Poster presented at the Hydrologic Sciences Symposium, University of Colorado at Boulder, March 13 2011. 
            \item \textit{Reclamation Review of Stochastic Streamflow Simulation at Interannual and Interdecadal Time Scales and Implications to Water Resources Management: Project overview}. Presented at the Seasonal to Year-Two Colorado River Streamflow Prediction Workshop, Colorado Basin River Forecast Center, Salt Lake City, Utah, March 21, 2011
            \item \textit{Experiences with Policy Development and Forecasting for the Midterm Probabilistic Model}. Presented at the RiverWare Users Group Meeting, Febrary 11th, 2010. 
            \item \textit{Reclamation Review of Stochastic Streamflow Simulation at Interannual and Interdecadal Time Scales and Implications to Water Resources Management: Past, Present and Future Work}. Presented to the Colorado River Basin Hydrology Working Group, October 5th, 2009. 
            \item \textit{The wonderful world of R}. Seminar, Humboldt State Unversity, 26 February 2009
            \item \textit{What the heck is LATEX?} Seminar, Humboldt State University, September 18 2008
            \item \textit{A Multi-Site Streamflow Forecast Framework: Application to the Upper Colorado River Basin}. AGU Fall Meeting H32E: Using Climate Information for Forecast Applications in Hydrology, Water and Energy Management, and Other Sectors II, August 9, 2007.
        \end{cvlist}
    \end{cv}
\end{document}